\vspace{-0.3em}
\bibliographystyle{abbrv}
\begin{thebibliography}{99}

\bibitem{AS 2019}
  Matteo Acclavio and Lutz Straßburger. On Combinatorial Proofs for Modal Logic. In \textit{International Conference on Automated Reasoning with Analytic Tableaux and Related Methods}, London, 2019. Springer.

\bibitem{BT 2001}
  Kai Brünnler and Alwen Tiu. A local system for classical logic. In R. Nieuwenhuis and A. Voronkov, editors, \textit{LPAR 2001}, volume 2250 of \textit{Lecture Notes in Artificial Intelligence}, pages 347-361, 2001. Springer.

\bibitem{Gentzen 1935}
  Gerhard Gentzen. Investigations into logical deduction. In M. E. Szabo, editor, \textit{The Collected Papers of Gerhard Gentzen}, pages 68-131. North-Holland, Amsterdam, 1935.

\bibitem{Hughes 2006}
  Dominic J. D. Hughes. Proofs without syntax. \textit{Annals of Mathematics}, 164(3):1065-1076, 2006.

\bibitem{Hughes 2015}
  Dominic J. D. Hughes.  Unification nets: canonical proof net quantifiers. In \textit{Proc. LICS '18}, 2018.

\bibitem{Hughes 2019}
  Dominic J. D. Hughes. First-order proofs without syntax. Available at arXiv.org, 2019.

\bibitem{RS 2019}
  Benjamin Ralph and Lutz Straßburger. Towards a combinatorial proof theory. In
		\textit{International Conference on Automated Reasoning with
		Analytic Tableaux and Related Methods}, London, 2019. Springer.

\bibitem{Retore 2003}
  Christian Retoré. Handsome proof-nets: perfact matchings and cographs. \textit{Theoretical Computer Science}, 294(3):473-488, 2003.

\bibitem{Strassburger 2007}
	Lutz Straßburger. A characterization of medial as rewriting rule. In
		\textit{International Conference on Rewriting Techniques and
		Applications}, pages 344-358. Springer, 2007.

\end{thebibliography}
